Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-14 Paperfolder/Paperfolder.Rmd
about to send to Yatsuya

  To further examine the relationship between milk intake and stroke mortality among the Japanese population. We used 

@@

Dairy food, especially milk has been recommended to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016]. More intuitive interpretation for a decreasing risk would be possible if we were able to compute the exact probability for people who had milk intake may had lower hazard of dying from stroke compared with those who never drank milk at all. For general public/media reporting, concept of hazard in epidemiological studies could still sometimes be challenging to be understood or misinterpreted since hazard is formally defined as the probability of the occurrence of an event at a given time point [@collett2015modelling]. Usually, authors of epidemiological papers would tend to use "risk" instead of "hazard" or interchangeably. However, it would still possibly be mixed up with "risk" that only contain pure meaning of "probability of an event" without redefining a point or a period of time in cross-sectional settings. For better understanding and interpretation of the findings from data that researchers endeavored to collect, statistical literature have provided plenty of choices that could help us better communicate with each other. Another approach of comparing the time-to-event survival probabilities between different groups would be to model the time before observing an event rather than the hazard which always required the assumption of a proportional hazard to be met. Accelerated failure time models are among these convenient tools that would avoid worrying about the assumption of proportional hazard and directly show how faster/slower that one individual in an exposure group might have an event compared to others among different exposure groups [@Wei1992].

>>>>

  The aim was to further examine the relationship between milk intake and stroke mortality among the Japanese population. We used data from the Japan Collaborative Cohort Study to estimate the posterior acceleration factors (AF) as well as the hazard ratios (HR) comparing individuals with different milk intake frequencies against those who never consumed milk at the study baseline. These estimations were computed through a series of Bayesian survival models that employed a Markov Chain Monte Carlo simulation process. 100000 posterior samples for each individual were generated separately through four independent chains after model convergency were confirmed. Posterior probabilites that daily milk consumers had lower hazard or delayed mortality from strokes compared to non-consumers was 99.0% and 78.0% for men and women, respectively. Accordingly, the estimated posterior means of AF and HR for daily milk consumers were 0.88 (95% Credible Interval, CrI: 0.81, 0.96) and 0.80 (95% CrI: 0.69, 0.93) for men and 0.97 (95% CrI: 0.88, 1.10) and 0.95 (95% CrI: 0.80, 1.17) for women.

@@

Dairy food, especially milk has been recommended to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016]. More intuitive interpretation for a decreasing risk would be possible if we were able to compute the exact probability for people who had milk intake may had lower hazard of dying from stroke compared with those who never drank milk at all. For general public/media reporting, concept of hazard in epidemiological studies could still sometimes be challenging to be understood or misinterpreted since hazard is formally defined as the probability of the occurrence of an event at a given time point [@collett2015modelling]. Usually, authors of epidemiological papers would tend to use "risk" instead of "hazard" or interchangeably. However, it would still possibly be mixed up with "risk" that only contain pure meaning of "probability of an event" without redefining a point or a period of time in cross-sectional settings. For better understanding and interpretation of the findings from data that researchers endeavored to collect, statistical literature have provided plenty of choices that could help us better communicate with each other. Another approach of comparing the time-to-event survival probabilities between different groups would be to model the time before observing an event rather than the hazard which always required the assumption of a proportional hazard to be met. Accelerated failure time models are among these convenient tools that would avoid worrying about the assumption of proportional hazard and directly showing how faster/slower one individual in an exposure group might have an event compared to others among different exposure groups [@Wei1992].

### 2020-07-14 Paperfolder/Paperfolder.tex
about to send to Yatsuya

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{To further examine the relationship between milk intake and
stroke mortality among the Japanese population. We used}

@@

Dairy food, especially milk has been recommended to reduce stroke risk
by nearly 7\% for each 200 g increment of daily consumption
\citep{DeGoede2016}. More intuitive interpretation for a decreasing risk
would be possible if we were able to compute the exact probability for
people who had milk intake may had lower hazard of dying from stroke
compared with those who never drank milk at all. For general
public/media reporting, concept of hazard in epidemiological studies
could still sometimes be challenging to be understood or misinterpreted
since hazard is formally defined as the probability of the occurrence of
an event at a given time point \citep{collett2015modelling}. Usually,
authors of epidemiological papers would tend to use ``risk'' instead of
``hazard'' or interchangeably. However, it would still possibly be mixed
up with ``risk'' that only contain pure meaning of ``probability of an
event'' without redefining a point or a period of time in
cross-sectional settings. For better understanding and interpretation of
the findings from data that researchers endeavored to collect,
statistical literature have provided plenty of choices that could help
us better communicate with each other. Another approach of comparing the
time-to-event survival probabilities between different groups would be
to model the time before observing an event rather than the hazard which
always required the assumption of a proportional hazard to be met.
Accelerated failure time models are among these convenient tools that
would avoid worrying about the assumption of proportional hazard and
directly show how faster/slower that one individual in an exposure group
might have an event compared to others among different exposure groups
\citep{Wei1992}.

>>>>

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{The aim was to further examine the relationship between milk
intake and stroke mortality among the Japanese population. We used data
from the Japan Collaborative Cohort Study to estimate the posterior
acceleration factors (AF) as well as the hazard ratios (HR) comparing
individuals with different milk intake frequencies against those who
never consumed milk at the study baseline. These estimations were
computed through a series of Bayesian survival models that employed a
Markov Chain Monte Carlo simulation process. 100000 posterior samples
for each individual were generated separately through four independent
chains after model convergency were confirmed. Posterior probabilites
that daily milk consumers had lower hazard or delayed mortality from
strokes compared to non-consumers was 99.0\% and 78.0\% for men and
women, respectively. Accordingly, the estimated posterior means of AF
and HR for daily milk consumers were 0.88 (95\% Credible Interval, CrI:
0.81, 0.96) and 0.80 (95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI:
0.88, 1.10) and 0.95 (95\% CrI: 0.80, 1.17) for women.}

@@

Dairy food, especially milk has been recommended to reduce stroke risk
by nearly 7\% for each 200 g increment of daily consumption
\citep{DeGoede2016}. More intuitive interpretation for a decreasing risk
would be possible if we were able to compute the exact probability for
people who had milk intake may had lower hazard of dying from stroke
compared with those who never drank milk at all. For general
public/media reporting, concept of hazard in epidemiological studies
could still sometimes be challenging to be understood or misinterpreted
since hazard is formally defined as the probability of the occurrence of
an event at a given time point \citep{collett2015modelling}. Usually,
authors of epidemiological papers would tend to use ``risk'' instead of
``hazard'' or interchangeably. However, it would still possibly be mixed
up with ``risk'' that only contain pure meaning of ``probability of an
event'' without redefining a point or a period of time in
cross-sectional settings. For better understanding and interpretation of
the findings from data that researchers endeavored to collect,
statistical literature have provided plenty of choices that could help
us better communicate with each other. Another approach of comparing the
time-to-event survival probabilities between different groups would be
to model the time before observing an event rather than the hazard which
always required the assumption of a proportional hazard to be met.
Accelerated failure time models are among these convenient tools that
would avoid worrying about the assumption of proportional hazard and
directly showing how faster/slower one individual in an exposure group
might have an event compared to others among different exposure groups
\citep{Wei1992}.
